Estimating the Effect of Urban Green Spaces on Residential House Prices in Amsterdam

### 2023-04-14 Paper/Term Project - Grings, Nauta, Nibbering.Rmd
paper update

  Results of the local regression model revealed that urban green spaces were significantly associated with residental house prices at a 300m spatial scale (p < 0.05). Here, property premiums per m2 ranged from -82,657.5 to 125,978.4 euros for each unit increase in the vegetation index. This result aligns with previous studies [23, 36, 39, 40]. One explanation for this wide range might be related to the direct-use value placed on these areas [23]. In other words, particular green areas might attract more residents to benefit from the perceived value of greenness, prompting more people to purchase houses nearby [44]. Hence, highlighting the spatial variability and non-stationary nature of the association of interest, as illustrated in Appendix II. Finally, the findings of this study provide empirical evidence of the capitalisation of greenness characteristics in residential real-estate prices. \linebreak

@@

```{=latex}
\begin{figure}[]
  \centering
  \includegraphics[width=\linewidth]{figures/Economic_Value_Urban_Green_clip.png}
  \caption{Overview of statistically significant (p < 0.05) urban green space coefficients at a 300m spatial scale in Amsterdam.}
\end{figure}
```

@@

# Appendix I

@@

# Appendix II

```{=latex}
\begin{figure}[ht]
  \centering
  \includegraphics[width=.8\linewidth]{figures/NDVI_clip.png}
  \caption{Overview of NDVI values in Amsterdam with a 300m Spatial Scale}
\end{figure}
```

>>>>

Results of the local regression model revealed that urban green spaces were significantly associated with residential house prices at a 300m spatial scale (p < 0.05). Here, property premiums per m2 ranged from -82,657.5 to 125,978.4 euros for each unit increase in the vegetation index. This result aligns with previous studies [23, 36, 39, 40]. One explanation for this wide range might be related to the direct-use value placed on these areas [23]. In other words, particular green areas might attract more residents to benefit from the perceived value of greenness, prompting more people to purchase houses nearby [44]. Hence, highlighting the spatial dependent and non-stationary nature of the association of interest, as illustrated in Appendix II. Finally, the findings of this study provide empirical evidence of the capitalisation of greenness characteristics in residential real-estate prices. \linebreak

@@

```{=latex}
\begin{figure}[]
  \centering
  \includegraphics[width=\linewidth]{figures/Economic_Value_Urban_Green.png}
  \caption{Overview of statistically significant (p < 0.05) urban green space coefficients at a 300m spatial scale in Amsterdam.}
\end{figure}
```

@@

# Appendix I - Hedonic Pricing Model Results

@@

# Appendix II – Residential House Prices and Urban Green Spaces in Amsterdam

```{=latex}
\begin{figure}[ht]
  \centering
  \includegraphics[width=.8\linewidth]{figures/Amsterdam_house_prices_sqm.png}
  \caption{Overview of residential house-prices (top) and mean NDVI at a 300m spatial scale (bottom) in Amsterdam.}
\end{figure}
```
